---
title: "Wave-Function Anomaly Detection"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
library(data.table)
library(h2o)
library(caret)
tidymodels_prefer()
```

## Data import

The audited workflow uses project-relative paths. See `data/README.md` for the expected layout.

```{r}
seed <- 43111
set.seed(seed)

data_path <- file.path("data", "wave_functions.csv")
if (!file.exists(data_path)) {
  stop("Missing data/wave_functions.csv. See data/README.md for the expected layout.")
}

d <- fread(
  data_path,
  header = FALSE,
  nrows = 800000,
  skip = 1700000
) %>%
  select(1:113) %>%
  rename(Target = V113) %>%
  mutate(
    Target = factor(
      if_else(Target == 0, "Smooth", "Anomaly"),
      levels = c("Anomaly", "Smooth")
    )
  ) %>%
  as_tibble()

if (ncol(d) != 113) {
  stop("Expected 112 predictors plus one target column.")
}
```

## Sampling and hold-out split

```{r}
set.seed(seed)
df <- d %>% slice_sample(prop = 0.003)

set.seed(seed)
df_split <- initial_split(df, prop = 0.75, strata = Target)
df_train_raw <- training(df_split)
df_test_raw <- testing(df_split)
```

## Training-only preprocessing

All data-dependent preprocessing is learned from the training partition once. The fitted recipe is then reused unchanged on test and validation data.

```{r}
preprocess_recipe <- recipe(Target ~ ., data = df_train_raw) %>%
  step_nzv(all_numeric_predictors()) %>%
  step_lincomb(all_numeric_predictors()) %>%
  step_corr(all_numeric_predictors(), threshold = 0.90) %>%
  step_YeoJohnson(all_numeric_predictors()) %>%
  step_normalize(all_numeric_predictors())

preprocess_fit <- prep(preprocess_recipe, training = df_train_raw)
df_train <- bake(preprocess_fit, new_data = NULL)
df_test <- bake(preprocess_fit, new_data = df_test_raw)
```

## H2O autoencoder

The target remains in the frame for bookkeeping but is excluded explicitly from the autoencoder predictors by name. The autoencoder configuration is fixed before held-out evaluation.

```{r}
h2o_instance <- h2o.init(max_mem_size = "6g")

train_h2o <- as.h2o(df_train, destination_frame = "wave_train")
test_h2o <- as.h2o(df_test, destination_frame = "wave_test")
predictor_columns <- setdiff(names(train_h2o), "Target")

if (length(predictor_columns) < 2) {
  stop("Preprocessing left too few predictors for representation learning.")
}

autoencoder <- h2o.deeplearning(
  x = predictor_columns,
  training_frame = train_h2o,
  autoencoder = TRUE,
  standardize = FALSE,
  shuffle_training_data = FALSE,
  reproducible = TRUE,
  seed = seed,
  hidden = c(64, 16, 4),
  activation = "Tanh",
  sparse = TRUE,
  sparsity_beta = 0.01,
  epochs = 100
)

print(autoencoder)
```

## Learned representations

The final hidden layer is a four-dimensional bottleneck. It is learned from the outer training partition only; held-out test rows are transformed by the already-fitted autoencoder.

```{r}
train_embedding <- h2o.deepfeatures(autoencoder, train_h2o, layer = 3) %>%
  as.data.frame() %>%
  bind_cols(Target = df_train$Target)

test_embedding <- h2o.deepfeatures(autoencoder, test_h2o, layer = 3) %>%
  as.data.frame() %>%
  bind_cols(Target = df_test$Target)
```

## Fixed XGBoost baseline

The downstream classifier uses a deliberately **fixed, pre-specified configuration**. Hyperparameters are not tuned with cross-validation on an embedding learned from all outer-training rows, avoiding the earlier mismatch where classifier validation folds had already influenced unsupervised preprocessing and representation learning. The held-out test partition is the only performance-evaluation set.

```{r}
embedding_predictors <- ncol(train_embedding) - 1L

xgb_spec <- boost_tree(
  trees = 500,
  tree_depth = 4,
  learn_rate = 0.05,
  loss_reduction = 0,
  min_n = 5,
  sample_size = 0.80,
  mtry = embedding_predictors
) %>%
  set_engine("xgboost", nthread = 1, seed = seed) %>%
  set_mode("classification")

xgb_workflow <- workflow() %>%
  add_recipe(recipe(Target ~ ., data = train_embedding)) %>%
  add_model(xgb_spec)

set.seed(seed)
final_model <- fit(xgb_workflow, data = train_embedding)
```

## Held-out evaluation

```{r}
test_predictions <- predict(final_model, test_embedding)

caret::confusionMatrix(
  test_predictions$.pred_class,
  test_embedding$Target,
  mode = "everything"
)
```

## Optional external validation

Any CSV files under `data/validation/` are processed using the already-fitted recipe, autoencoder and classifier. Validation data are never used to refit preprocessing, representation learning or the classifier.

```{r}
validation_dir <- file.path("data", "validation")

if (dir.exists(validation_dir)) {
  validation_files <- list.files(validation_dir, pattern = "\\.csv$", full.names = TRUE)

  for (validation_path in validation_files) {
    validation_raw <- fread(validation_path, header = FALSE)

    if (ncol(validation_raw) < 113) {
      warning(sprintf("Skipping %s: fewer than 113 columns.", validation_path))
      next
    }

    validation_raw <- validation_raw[, 1:113]
    names(validation_raw)[113] <- "Target"
    validation_raw <- validation_raw %>%
      mutate(
        Target = factor(
          if_else(Target == 0, "Smooth", "Anomaly"),
          levels = levels(df_train_raw$Target)
        )
      ) %>%
      as_tibble()

    validation_processed <- bake(preprocess_fit, new_data = validation_raw)
    validation_x <- validation_processed %>% select(-Target)
    validation_h2o <- as.h2o(validation_x)

    validation_embedding <- h2o.deepfeatures(
      autoencoder,
      validation_h2o,
      layer = 3
    ) %>%
      as.data.frame() %>%
      bind_cols(Target = validation_processed$Target)

    validation_predictions <- predict(final_model, validation_embedding)

    print(basename(validation_path))
    print(
      caret::confusionMatrix(
        validation_predictions$.pred_class,
        validation_embedding$Target,
        mode = "everything"
      )
    )
  }
}
```

## Shut down H2O

```{r}
h2o.shutdown(prompt = FALSE)
```

## Session information

```{r}
sessionInfo()
```
